Sensitivity Analysis

### 2024-10-11 Article_Sensitivity_Analsysis-Chamomile.tex
11.10

% ---------------------------------------------------------------
% Preamble
% ---------------------------------------------------------------
%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}
\documentclass[a4paper,fleqn]{cas-dc}
%\documentclass[a4paper]{cas-dc}
%\documentclass[a4paper]{cas-sc}
% ---------------------------------------------------------------
% Make margins bigger to fit annotations. Use 1, 2 and 3. TO be removed later
%\paperwidth=\dimexpr \paperwidth + 6cm\relax
%\oddsidemargin=\dimexpr\oddsidemargin + 3cm\relax
%\evensidemargin=\dimexpr\evensidemargin + 3cm\relax
%\marginparwidth=\dimexpr \marginparwidth + 3cm\relax
% -------------------------------------------------------------------- 
% Packages
% --------------------------------------------------------------------
% Figure packages
\usepackage{graphicx,float}
\usepackage{adjustbox}
% Text, input, formatting, and language-related packages
\usepackage[T1]{fontenc}
\usepackage{subcaption}

@@

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study investigates the process of chamomile oil extraction from chamomile flowers. A parameter-distributed model, consisting of a set of partial differential equations, is used to describe the governing mass transfer phenomena between solid and fluid phases under supercritical conditions using carbon dioxide as the solvent. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated using the Peng-Robinson equation of state. Laboratory experiments were conducted under various, but constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s. Different sensitivity analysis methods can be applied to assess the robustness of the model parameters and their influence on the process model. Local sensitivity analysis investigates the impact of infinitesimally small changes in model parameters and controls on model output. This study focuses on analysing the effect of pressure on the model state space and extraction yield.

@@

Sensitivity analysis is a tool used to understand how model parameters affect its output. The presented formulation involves derivative-based local sensitivity analysis of the model solution with respect to selected parameters and controls. This work implemented the automatic differentiation to derive the sensitivity equations. The local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions. In the case of dynamical systems, local sensitivity analysis provides a time series describing how that dependency evolves.

The local sensitivity analysis can be performed with respect to any model parameter, but this work focuses on the effect of pressure increase. At selected operating conditions ($35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s), the pressure increase enhances the mass transfer, which leads to faster loss of solute from particles and consequently to negative sensitivities in the solid phase. Analogously, the sensitivities in the fluid phase are characterised by positive deviations, which indicates that more solute is transported to the fluid phase. As a result, the extraction yield is improved and characterised by positive sensitivities. As the results of the local sensitivity analysis depends on the operating point, the analysis was repeated at different nominal pressures. It can be observed that system responses at low-pressures are stronger than at high-pressures. This behaviour can be explained by more rapid changes of the solvent properties close to the critical point and lower process efficiency at low-pressure.

Local sensitivity analysis can provide valuable information by identifying which parameters are influential and how these influence changes over time. Sensitivity analysis can highlight discrepancies between model predictions and actual experimental results. Identifying unexpected relationships or non-linearities can prompt further investigation and refinement of the process model. Sensitivity analysis can inform the design of future experiments by indicating which parameters should be varied and monitored.

% ===================================================
% Bibliography
% ===================================================
%% Loading bibliography style file
%\clearpage
%\bibliographystyle{model1-num-names}
\bibliographystyle{unsrtnat}
\bibliography{mybibfile}

@@

>>>>

% ---------------------------------------------------------------
% Preamble
% ---------------------------------------------------------------
%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}
\documentclass[a4paper,fleqn]{cas-dc}
%\documentclass[a4paper]{cas-dc}
%\documentclass[a4paper]{cas-sc}
% ---------------------------------------------------------------
% Make margins bigger to fit annotations. Use 1, 2 and 3. TO be removed later
%\paperwidth=\dimexpr \paperwidth + 6cm\relax
%\oddsidemargin=\dimexpr\oddsidemargin + 3cm\relax
%\evensidemargin=\dimexpr\evensidemargin + 3cm\relax
%\marginparwidth=\dimexpr \marginparwidth + 3cm\relax
% -------------------------------------------------------------------- 
% Packages
\usepackage[switch]{lineno}
\linenumbers

% --------------------------------------------------------------------
% Figure packages
\usepackage{graphicx,float}
\usepackage{adjustbox}
% Text, input, formatting, and language-related packages
\usepackage[T1]{fontenc}
\usepackage{subcaption}

\usepackage{nomencl}
\makenomenclature

\usepackage{etoolbox}
\renewcommand\nomgroup[1]{%
	\item[\bfseries
	\ifstrequal{#1}{A}{}{%
		\ifstrequal{#1}{B}{Greek symbols}{%
			\ifstrequal{#1}{C}{Abberivations}{
	}}}%
	]}
\newcommand{\nomunit}[1]{%
	\renewcommand{\nomentryend}{\hspace*{\fill}#1}}

@@

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study investigates the process of chamomile oil extraction from chamomile flowers. A parameter-distributed model, consisting of a set of partial differential equations, is used to describe the governing mass transfer phenomena between solid and fluid phases under supercritical conditions using carbon dioxide as the solvent. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The {\color{blue}flow of carbon dioxide} is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated using the Peng-Robinson equation of state. Laboratory experiments were conducted under various, but constant operating conditions. $30 - 40~^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s. {\color{blue}The local sensitivity analysis method was applied to evaluate the model parameters' robustness by investigating the impact of infinitesimally small changes in model parameters and controls on model outputs}. This study focuses on analysing the effect of pressure on the model state space and extraction yield.

@@

Sensitivity analysis is a tool used to understand how model parameters affect its output. The presented formulation involves derivative-based local sensitivity analysis of the model solution with respect to selected parameters and controls. This work implemented the automatic differentiation to derive the sensitivity equations. The local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions. In the case of dynamic systems, the outcome of local sensitivity analysis quantifies how the state of the system or its output varies in time with respect to small perturbations in parameters.

%The local sensitivity analysis can be performed with respect to any model parameter, but this work focuses on the effect of pressure increase. At selected operating conditions( $35^\circ C$ and $5\cdot 10^{-5}$ kg/s), the pressure increase enhances the mass transfer, which leads to faster mass transfer from particles and consequently to negative sensitivities in the solid phase. Analogously, the sensitivities in the fluid phase are characterised by positive deviations, which indicates that more solute is transported to the fluid phase. As a result, the extraction yield is improved and characterised by positive sensitivities. As the results of the local sensitivity analysis depends on the operating point, the analysis was repeated at different nominal pressures. It can be observed that system responses at low-pressures are stronger than at high-pressures. This behaviour can be explained by rapid changes of the solvent properties close to the critical point.

{\color{blue}Although local sensitivity analysis can be performed with respect to any model parameter, this study focuses specifically on the effect of increasing pressure. Under the selected operating conditions ($35~^\circ C$ and $5 \times 10^{-5}$ kg/s), it was observed for all the cases that the pressure increment enhances mass transfer, leading to a more faster mass transfer of solute from the particles. Consequently, the negative sensitivities can be observed in the diagram for the solid phase. The corresponding response in the fluid phase is characterized by positive-valued sensitivities, indicating that more amount of solute is transported into the fluid phase. As a result, the extraction yield is improved and characterized by positive sensitivities. Given that the results of the local sensitivity analysis depend on the operating point, the analysis was repeated at different pressures. It was observed that the system responses at low pressures are stronger than those at higher pressures. This behaviour can be explained by the rapid changes in solvent properties occurring near the critical point of CO$_2$}.

Local sensitivity analysis results provide valuable information by identifying which parameters are influential and how these influence changes over time. One application of the sensitivity analysis is to spot discrepancies between model predictions and actual experimental results. Identifying unexpected system responses prompts further investigation and refinement of the process model. Sensitivity analysis results can be used to design future experiments by indicating which parameters should be varied and monitored. Moreover, the parameters which are characterized by low sensitivity can be subject of model reduction.

\section*{Acknowledgement} 
This work was supported by NovelBaltic, CEForestry (IBC), BIO4P (BF)

% ===================================================
% Bibliography
% ===================================================
%% Loading bibliography style file
%\clearpage
\newpage
%\bibliographystyle{model1-num-names}
\bibliographystyle{unsrtnat}
\bibliography{mybibfile}

@@

\newpage

\nomenclature[A]{\(P\)}{Pressure \nomunit{bar}}
\nomenclature[A]{\(T\)}{Temperature \nomunit{K}}
\nomenclature[A]{\(T_{in}\)}{Inlet temperature \nomunit{K}}
\nomenclature[A]{\(T_{out}\)}{Outlet temperature \nomunit{K}}
\nomenclature[A]{\(F\)}{Mass flow rate \nomunit{kg/s}}
\nomenclature[A]{\(u\)}{Superficial velocity \nomunit{m/s}}
\nomenclature[A]{\(v\)}{Linear velocity \nomunit{m/s}}
\nomenclature[A]{\(z\)}{Spatial direction \nomunit{m}}
\nomenclature[A]{\(e\)}{Internal energy \nomunit{J/kg}}
\nomenclature[A]{\(h\)}{Enthalpy \nomunit{J}}
\nomenclature[A]{\(t\)}{Time \nomunit{s}}
\nomenclature[A]{\(t_f\)}{Total extraction time \nomunit{s}}
\nomenclature[A]{\(t_0\)}{Initial extraction time \nomunit{s}}
\nomenclature[A]{\(A\)}{Total cross-section of the bed \nomunit{m$^2$}}
\nomenclature[A]{\(A_f\)}{Cross-section of the bed occupied by the fluid \nomunit{m$^2$}}
\nomenclature[A]{\(c_f\)}{Concentration of solute in the fluid phase \nomunit{kg/m$^3$}}
\nomenclature[A]{\(c_{f0}\)}{Initial concentration of solute in the fluid phase \nomunit{kg/m$^3$}}
\nomenclature[A]{\(c_f^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg/m$^3$}}
\nomenclature[A]{\(c_s\)}{Concentration of solute in the solid phase \nomunit{kg/m$^3$}}
\nomenclature[A]{\(c_{s0}\)}{Initial concentration of solute in the solid phase \nomunit{kg/m$^3$}}
\nomenclature[A]{\(c_s^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg$^3$}}
\nomenclature[A]{\(c_p\)}{Concentration of solute in the core of a pore \nomunit{kg/m$^3$}}
\nomenclature[A]{\(c_{pf}\)}{Concentration of solute at the pore opening \nomunit{kg/m$^3$}}
\nomenclature[A]{\(D_e^M\)}{Axial diffusion coefficient \nomunit{m$^2$/s}}
\nomenclature[A]{\(r_e\)}{Mass transfer kinetic term \nomunit{kg/m$^3$/s}}
\nomenclature[A]{\(L\)}{Length of the fixed bed \nomunit{m}}
\nomenclature[A]{\(S\)}{Sensitivity equations}
\nomenclature[A]{\(\textbf{G}\)}{Augmented system}
\nomenclature[A]{\(\dot{S}\)}{Time derivative of the sensitivity equations}
\nomenclature[A]{\(\bar{S}\)}{Sensitivity matrix}
\nomenclature[A]{\(\bar{J}_x\)}{Jacobian matrix with respect to the state variables}
\nomenclature[A]{\(\bar{J}_\Theta\)}{Jacobian matrix with respect to the parameters}
%\nomenclature[A]{\(\mathcal{L}\)}{Log-likelihood function}
\nomenclature[A]{\(l\)}{Characteristic dimension of particles \nomunit{m}}
\nomenclature[A]{\(D_i\)}{Internal diffusion coefficient \nomunit{m$^2$/s}}
\nomenclature[A]{\(D_i^R\)}{Reference value of internal diffusion coefficient \nomunit{m$^2$/s}}
\nomenclature[A]{\(r\)}{Particle radius \nomunit{m}}
\nomenclature[A]{\(k_p\)}{Volumetric partition coefficient \nomunit{-}}
\nomenclature[A]{\(k_m\)}{Mass partition coefficient \nomunit{-}}
\nomenclature[A]{\(y\)}{Extraction yield \nomunit{g}}
\nomenclature[A]{\(Y\)}{Yield measurement \nomunit{g}}
\nomenclature[A]{\(x\)}{State vector}
\nomenclature[A]{\(G\)}{Vector of discretized differential equations}
\nomenclature[A]{\(p\)}{Probability distribution model \nomunit{-}}
\nomenclature[A]{\(R_e\)}{Reynolds number \nomunit{-}}

\nomenclature[B]{\(\rho_f\)}{Fluid density \nomunit{kg/m$^3$}}
\nomenclature[B]{\(\Phi\)}{Bed porosity \nomunit{-}}
\nomenclature[B]{\(\rho_s\)}{Bulk density of the solid \nomunit{kg/m$^3$}}
\nomenclature[B]{\(\mu\)}{Sphericity coefficient \nomunit{-}}
\nomenclature[B]{\(\gamma\)}{Decay function \nomunit{-}}
\nomenclature[B]{\(\Upsilon\)}{Decay coefficient \nomunit{-}}
\nomenclature[B]{\(\Theta\)}{Parameter space}
\nomenclature[B]{\(\theta\)}{Vector of unknown parameters}
\nomenclature[B]{\(\epsilon\)}{Unobservable error \nomunit{g}}
\nomenclature[B]{\(\sigma\)}{Standard deviation \nomunit{g}}

\nomenclature[C]{BIC}{Broke-and-Intact Cell model}
%\nomenclature[C]{MLE}{Maximum Likelihood Estimation}
\nomenclature[C]{SFE}{Supercritical Fluid Extraction}
\nomenclature[C]{HBD}{Hot Ball Diffusion}
\nomenclature[C]{SC}{Shrinking Core}

\printnomenclature

### 2024-10-11 Sections/Literature_Review.tex
11.10

	This study aims to analyze the influence of changes in operating conditions on the process model described in {\color{red}article 1}. Sensitivity analysis is applied to examine the impact of model parameters or controls on the model output. The results of sensitivity analysis can be used to identify sources of uncertainty, simplify the model, or detect errors by revealing unexpected relationships between inputs and outputs. Various sensitivity analysis methods are available, including:

@@

	\citet{Hatami2024} performed a one-factor-at-a-time sensitivity analysis to assess the response of net present value to variations in technical and economic variables. Their study consists of two parts. The first part examines how net present value is influenced by changes in individual technical and economic parameters, keeping the extractor volume constant at 300 L. The second part investigates the effects of varying the extractor volume (from 1 to 600 L) on the project's overall profitability. Their findings indicate that the most influential factors on net present value include the price of the extract, interest rate, dynamic time, and project lifetime.

>>>>

	This study aims to analyze the influence of changes in operating conditions on the process model described by \citet{Sliczniuk2024}. Sensitivity analysis is applied to examine the impact of model parameters or controls on the model output. The results of sensitivity analysis can be used to identify sources of uncertainty, simplify the model, or detect errors by revealing unexpected relationships between inputs and outputs. Various sensitivity analysis methods are available, including:

@@

	\citet{Hatami2024} performed a one-factor-at-a-time sensitivity analysis to assess the response of net present value to variations in technical and economic variables. Their study consists of two parts. The first part examines how net present value is influenced by changes in individual technical and economic parameters, keeping the extractor volume constant at 300 L. The second part investigates the effects of varying the extractor volume (from 1 to 600 L) on the project's overall profitability. {\color{blue}The authors found that the raw material price, discount rate and residence time had the biggest impact on NPV}.
	%Their findings indicate that the most influential factors on net present value include the price of the extract, interest rate, dynamic time, and project lifetime.

### 2024-10-11 Sections/Model.tex
11.10

	As discussed by \citet{Anderson2023}, all flows are compressible, but some of them can be treated as incompressible when the Mach number is smaller than 0.3. This assumption leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow. The assumption allows for removing acoustic waves and large perturbations in density and/or temperature. In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.

@@

			The main advantage of this formulation is the presence of term $\partial P / \partial t $, which directly affects the system through the change of thermodynamic pressure.

@@

@@

			As explained in Chapters \ref{CH:Governing_equations_chapter}, at Low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound. Under such conditions, the term $\partial P/\partial t$ can be approximated by a difference equation, which describes the pressure change in the whole system. The pressure $P$ in the system is considered a state variable, while the pressure in the new time-step $P_{in}$ is considered a control variable.

>>>>

	As discussed by \citet{Anderson2023}, all flows are compressible, but some of them can be treated as {\color{blue}incompressible since the velocities are low}. This assumption leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow. The assumption allows for removing acoustic waves and large perturbations in density and/or temperature. In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant along the $z-$ direction.

@@

			%The main advantage of this formulation is the presence of term $\partial P / \partial t $, which directly affects the system through the change of thermodynamic pressure.

@@

			where $\alpha$ is defined as $\left( 1+\kappa \left( 1 - \sqrt{T_r} \right) \right)^2$, $T_r$ is the reduced temperature, $P_r$ is the reduced pressure, $Z$ is the compressibility factor, $\kappa$ is a quadratic function of the acentric factor and $B$ is calculated as $0.07780\frac{P_r}{T_r}$.

@@

			As explained in Chapters \ref{CH:Governing_equations_chapter}, {\color{blue}this low velocity region, pressure is}, nearly constant due to the small pressure wave propagation that occurs at the speed of sound. Under such conditions, the term $\partial P/\partial t$ can be approximated by a difference equation, {\color{blue}describing} the pressure change in the whole system. The pressure $P$ in the system is considered a state variable, while the pressure in the new time-step $P_{in}$ is considered a control variable.

### 2024-10-11 Sections/Saturation.tex
11.10

	The empirical correlations for $D_i$ and $\Upsilon$ were derived by {\color{red}article 1} and validated for temperatures between $30 - 40^\circ C$, pressures between $100 - 200$ bar, and mass flow rates between $3.33-6.67 \cdot 10^{-5}$ kg/s. Figures \ref{fig:Correlation_Di} and \ref{fig:Correlation_Gamma} show the results of multiple linear regression applied to solutions of parameter estimation and selected independent variables. The region marked with the white dashed line represents the confidence region, where the model has been tested. Both correlations should be equal of greater than zero, to avoid unphysical behaviour such as the reverse mass transfer. The multiple linear regression functions are combined with the rectifier function to ensure the non-negativity.

>>>>

	The empirical correlations for $D_i$ and $\Upsilon$ were derived by \citet{Sliczniuk2024} and validated for temperatures between $30 - 40~^\circ C$, pressures between $100 - 200$ bar, and mass flow rates between $3.33-6.67 \cdot 10^{-5}$ kg/s. Figures \ref{fig:Correlation_Di} and \ref{fig:Correlation_Gamma} show the results of multiple linear regression applied to solutions of parameter estimation and selected independent variables. The region marked with the white dashed line represents the confidence region, where the model has been tested. Both correlations should be equal of greater than zero, to avoid unphysical behaviour such as the reverse mass transfer. The multiple linear regression functions are combined with the rectifier function to ensure the non-negativity.

### 2024-10-11 Sections/Sensitivity_Pressure.tex
11.10

	As discussed in Chapter \ref{CH:Governing_equations_chapter}, a small pressure wave propagates at the speed of sound relative to the flow. When the flow velocity is relatively low, pressure changes are hydrodynamic (resulting from velocity motion) rather than thermodynamic. The Low Mach number assumption allows for the instant propagation of thermodynamic pressure throughout the system, enabling a single pressure value to be considered for the entire system. In response to a pressure change, the energy equation experiences a simultaneous deviation across the entire spatial domain. This pressure change impacts the fluid's temperature within the computational domain, while boundary values are constrained by conditions specified at the domain's extremes. Dirichlet boundary conditions impose a fixed temperature value at the inlet, creating a thermal gradient that propagates through the system. On the other hand, Neumann boundary conditions specify the heat flux at the boundaries. In this study, zero Neumann boundary conditions were applied to ensure that the temperatures at the inlet, outlet, and within the extractor vary uniformly in response to the pressure change.

	Figure \ref{fig:Sensitivty_P_CS} illustrates the sensitivity of solute concentration in the solid phase to pressure changes. As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, indicating that increased pressure reduces the fluid's velocity. This results in an extended residence time, allowing for longer interaction between the solute and solvent.	Initially, the extraction process operates in the kinetic-controlled regime, where the concentration gradient is high, and solute solubility is the limiting factor. As noted in [article 1], the system is considered far from saturation, which explains the low initial system response. This low initial response was also observed in the sensitivity analysis by \citet{Fiori_2007}. The system's response becomes more pronounced as the concentration gradient decreases and the extraction shifts from the kinetic-controlled to the diffusion-controlled regime. The negative sensitivity indicates a faster solute loss from the solid phase, corresponding to enhanced mass transfer.  Over time, as the amount of solute decreases, it becomes a limiting factor, reducing the effect of pressure changes on the system. Eventually, the sensitivities approach zero asymptotically as the solute is washed out from the bed.

@@

	Figure \ref{fig:Sensitivty_P_CF} illustrates the sensitivity of solute concentration in the fluid phase to pressure changes. Compared to Figure \ref{fig:Sensitivty_P_CS}, the dynamic behaviour of fluid phase sensitivities is more apparent. Due to advection, the sensitivities move through the system similarly to the solute in the fluid phase.	Initially, the system response is low despite the pressure increase improving mass transfer, reflecting the previously discussed idle period. As the process continues, the sensitivities increase, indicating faster solute loss from the solid phase. The positive sensitivities show that more solute is being transported from the solid particles to the fluid. When the solute in the solid phase becomes a limiting factor, the extraction rate slows, and sensitivities decline to negative values, eventually approaching zero asymptotically.

@@

	As presented in Figure \ref{fig:Sensitivty_P_y}, higher sensitivities are observed for the low-pressure system. At lower pressures, the supercritical fluid has lower density and solvating power, which results in less efficient extraction as shown by data given in {\color{red}article 1}. Small changes in pressure at low pressures can significantly impact the solute's solubility and, consequently, the extraction yield. Moreover, near the critical point, small changes in pressure can lead to significant changes in the physical properties of the supercritical fluid, such as density and viscosity and consequently to higher sensitivity of the system state-space.

>>>>

	As discussed in Chapter \ref{CH:Governing_equations_chapter}, a small pressure wave propagates at the speed of sound relative to the flow. When the flow velocity is relatively low, pressure changes are hydrodynamic (resulting from velocity motion) rather than thermodynamic. {\color{blue}Low velocity results in the instant propagation} of thermodynamic pressure throughout the system, enabling a single pressure value to be considered for the entire system. In response to a pressure change, the energy equation experiences a simultaneous deviation across the entire spatial domain. This pressure change impacts the fluid temperature within the computational domain, while boundary values are constrained by conditions specified at the domain's extremes. Dirichlet boundary conditions impose a fixed temperature value at the inlet, creating a thermal gradient that propagates through the system. On the other hand, Neumann boundary conditions specify the heat flux at the boundaries. In this study, zero Neumann boundary conditions were applied to ensure that the temperatures at the inlet, outlet, and within the extractor vary uniformly in response to the pressure change.

	Figure \ref{fig:Sensitivty_P_CS} illustrates the sensitivity of solute concentration in the solid phase to pressure changes. As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, indicating that increased pressure reduces the fluid velocity. This results in an extended residence time, allowing for longer interaction between the solute and solvent.	Initially, the extraction process operates in the kinetic-controlled regime, where the concentration gradient is high, and solute solubility is the limiting factor. As noted by \citet{Sliczniuk2024}, the system is considered far from saturation, which explains the low initial system response. This low initial response was also observed in the sensitivity analysis by \citet{Fiori_2007}. The system's response becomes more pronounced as the concentration gradient decreases and the extraction shifts from the kinetic-controlled to the diffusion-controlled regime. {\color{blue}In Figure \ref{fig:Sensitivty_P_CS}, all $\frac{dc_s}{dP}$ values are negative, which indicates a faster mass transfer} from the solid phase, corresponding to enhanced mass transfer.  Over time, as the amount of solute decreases, it becomes a limiting factor, reducing the effect of pressure changes on the system. Eventually, the sensitivities approach zero asymptotically as the solute is washed out from the bed.

@@

	Figure \ref{fig:Sensitivty_P_CF} illustrates the sensitivity of solute concentration in the fluid phase to pressure changes. Compared to Figure \ref{fig:Sensitivty_P_CS}, the dynamic behaviour of fluid phase sensitivities is more apparent. Due to advection, the sensitivities move through the system similarly to the solute in the fluid phase.	Initially, the system response is low despite the pressure increase improving mass transfer, reflecting the previously discussed idle period. As the process continues, the sensitivities increase, indicating faster mass transfer from the solid phase. The corresponding improvement in the mass transfer from the solid particles to the fluid is represented by the positive values in Figure \ref{fig:Sensitivty_P_CF}. When the solute in the solid phase becomes a limiting factor, the extraction rate slows, and sensitivities eventually approaching zero asymptotically.

@@

	As presented in Figure \ref{fig:Sensitivty_P_y}, higher sensitivities are observed for the low-pressure system. At lower pressures, the supercritical fluid has lower density and solvating power, which results in less efficient extraction as shown by data given by \citet{Sliczniuk2024}. Small changes in pressure at low pressures can significantly impact the solute's solubility and, consequently, the extraction yield. Moreover, near the critical point, small changes in pressure can lead to significant changes in the physical properties of the supercritical fluid, such as density and viscosity and consequently to higher sensitivity of the system state-space.

### 2024-10-11 Sections/introduction_imp.tex
11.10

	This work builds upon the linear kinetic model suggested by \citet{Reverchon1996}, deriving fundamental governing equations to develop a comprehensive model for the chamomile oil extraction process. This model aims for control-oriented simplicity, assuming a semi-continuous operation within a cylindrical vessel. The process involves a supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract. Parameters such as pressure ($P$), feed flow rate ($F$) and inlet temperature ($T^{in}$) are adjustable and measurable, while the outlet temperature ($T^{out}$) and the amount of product at the outlet can only be monitored. Figure \ref{fig: SFE_drawing} presents a simplified process flow diagram.

>>>>

	This work builds upon the linear kinetic model suggested by \citet{Reverchon1996}, deriving fundamental governing equations to develop a comprehensive model for the chamomile oil extraction process. This model aims for control-oriented simplicity, assuming a semi-continuous operation within a cylindrical vessel. The process involves a supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract. Parameters such as pressure ($P$), feed flow rate ($F$) and inlet temperature ($T_{in}$) are adjustable and measurable, while the outlet temperature ($T_{out}$) and the amount of product at the outlet can only be monitored. Figure \ref{fig: SFE_drawing} presents a simplified process flow diagram.
